High-order cognition is supported by complex but compressible brain activity patterns

### 2023-03-01 paper/main.tex
added some notes, updated decoding/inflection figure, backing up progress

>>>>

other themes:
- predictability implies redundancy

- the structure of our brain patterns changes with cognitive task. maybe
something about flexibility or adaptability? why might some states benefit from
more compressibiilty or more informativeness?

- for a fixed set of "symbols" the information rate decreases as the signal is
compressed further. but our finding that each brain pattern component (symbol)
becomes more informative as cognitive richness increases suggests that the
"alphabet" of brain patterns is task dependent.

- representations themselves may also change with task demands (e.g., Mack et al, 2020)

- different brain networks appear to optimize in different ways, perhaps for different
cognitive tasks or operations.

\subsection*{Concluding remarks}

- something about the fundamental nature of brain activity and the neural basis of thought.
